Making Sequential Programs Deterministic

### 2019-03-22 design.tex
Move text, add new section header

%Method overriding and example
For method overriding, the usual rules apply for parameters and arguments i.e covariant subtyping for parameters
and contravariant subtyping for return types. Consider the example in Figure~\ref{code-invalid2} where method \<foo> of \<class X> is overridden
in \<class Y>.
\begin{figure}
	\begin{verbatim}
	class X {
	    @B int foo (@C int param) {}
	}
	class Y extends X {
	    @C int foo (@B int param) {}
	}
	\end{verbatim}
	\caption{Example: Invalid Method override}
	\label{code-invalid2}
\end{figure}

@@

@@

\subsection{Polymorphic annotations and special cases}
The underlying checker-framework on which we build our determinism checker has support for
polymorphic annotations. When a user writes a polymorphic annotation on a method signature or a type parameter,
it indicates that it could resolve to any type in the type system depending on how it is used.
In the determinism checker, we define a polymorphic annotation \<@PolyDet>.
One of the most common locations for a polymorphic annotation is at a method signature.
Consider the following method declaration annotated with polymorphic annotations
\begin{verbatim}
@PolyDet int foo (@PolyDet String param1, @PolyDet boolean param2) { }
\end{verbatim}
This indicates that method \<foo> can be called with arguments having any of the \codeid{@Det or @NonDet} type annotations 
(\<@OrderNonDet> is not allowed because it is invalid on primitive types). \<@PolyDet> resolves to the least upper bound of
the actual types on arguments. For instance, if this method is called as \codeid{foo(@Det String arg1, @NonDet boolean arg2)}, the 
checker framework resolves the method declaration as \codeid{@NonDet int foo(@NonDet String param1, @NonDet boolean param2)}
causing the return type to have the type annotation \<@NonDet>.

@@

>>>>

%Method overriding and example
For method overriding, the usual rules apply for parameters and arguments i.e covariant subtyping for parameters
and contravariant subtyping for return types. Consider the example in Figure~\ref{code-invalid2} where method \<foo> of \<class X> is overridden
in \<class Y>.
\begin{figure}
	\begin{verbatim}
	class X {
	    @B int foo(@C int param) {}
	}
	class Y extends X {
	    @C int foo(@B int param) {}
	}
	\end{verbatim}
	\caption{Example: Invalid Method override}
	\label{code-invalid2}
\end{figure}

@@

\subsection{Determinism}

The underlying checker-framework on which we build our determinism checker has support for
polymorphic annotations. When a user writes a polymorphic annotation on a method signature or a type parameter,
it indicates that it could resolve to any type in the type system depending on how it is used.
In the determinism checker, we define a polymorphic annotation \<@PolyDet>.
One of the most common locations for a polymorphic annotation is at a method signature.
Consider the following method declaration annotated with polymorphic annotations
\begin{verbatim}
@PolyDet int foo(@PolyDet String param1, @PolyDet boolean param2) { }
\end{verbatim}
This indicates that method \<foo> can be called with arguments having any of the \codeid{@Det or @NonDet} type annotations 
(\<@OrderNonDet> is not allowed because it is invalid on primitive types). \<@PolyDet> resolves to the least upper bound of
the actual types on arguments. For instance, if this method is called as \codeid{foo(@Det String arg1, @NonDet boolean arg2)}, the 
checker framework resolves the method declaration as \codeid{@NonDet int foo(@NonDet String param1, @NonDet boolean param2)}
causing the return type to have the type annotation \<@NonDet>.

@@

\subsection{Polymorphism extensions}

@@

\subsection{Differentiating binding and use}
